---
title: "Weight of Fish"
author: "Amee Rodrick"
date: "November 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Perch Model
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->


```{r}
# read in the fish
fishdata <- read.csv(file="Fish.csv", header=TRUE)
Perchdata <- filter(fishdata,Species=="Perch") %>% select(-Species)
```

Now Build our Models 

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perchdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### The best two regressors model for Perch is Height and Width.This is also the best overall model as measured by the Adjusted R-squared.


# Bream Model

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
# read in the fish
fishdata <- read.csv(file="Fish.csv", header=TRUE)
Breamdata <- filter(fishdata,Species=="Bream") %>% select(-Species)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Breamdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### The best two regressor model for Bream is Length2 and Height at about 92%. This is the best overall model for the Adjusted R-squared. 

## Smelt Model

```{r}
# read in the fish
fishdata <- read.csv(file="Fish.csv", header=TRUE)
Smeltdata <- filter(fishdata,Species=="Smelt") %>% select(-Species)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Smeltdata,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### The best two regressors models for Smelt is Length2 and Width at about 97% This is the best overall model for Adjusted R-squared..


# Discussion and  Final Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The relationship between all 3 fish has differences in all catagories height, width and length all the fish are different, Bream s length2 and height whereas smelt is length2 and width and perch is width and height.. theres is no match with any of the 3 fish. 



